Master Thesis

### 2013-07-02 gacg.tex
Typography changes near end of GACGs

\begin{description}
  \item[Extrinsic languages can be defined similarly to pangraphical
    languages] \hfill \\

@@

  \item[The three languages are increasingly constraining:
    $\mathcal{P}_{\mathcal{G}}(u) \subseteq \mathcal{E}_{\mathcal{G}}(u)
    \subseteq \mathcal{I}_{\mathcal{G}}(u)$] \hfill \\

@@

  \item[On arborescences, $\mathcal{P}_{\mathcal{G}}(u) =
    \mathcal{E}_{\mathcal{G}}(u)$.] \hfill \\

@@

  \item[The set of extrinsic languages is included in the set of
    pangraphical languages.] \hfill \\

@@

  \item[Is the set of pangraphical languages included in the set of
    extrinsic languages?] \hfill \\

>>>>

\begin{description}
  \item[Extrinsic languages can be defined similarly to pangraphical
    languages] \hfill

@@

  \vspace{0.5cm}

  \item[The three languages are increasingly constraining:
    $\mathcal{P}_{\mathcal{G}}(u) \subseteq \mathcal{E}_{\mathcal{G}}(u)
    \subseteq \mathcal{I}_{\mathcal{G}}(u)$] \hfill

@@

  \vspace{0.5cm}

  \item[On arborescences, $\mathcal{P}_{\mathcal{G}}(u) =
    \mathcal{E}_{\mathcal{G}}(u)$.] \hfill

@@

  \vspace{0.5cm}

  \item[The set of extrinsic languages is included in the set of
    pangraphical languages.] \hfill

@@

  \vspace{0.5cm}

  \item[Is the set of pangraphical languages included in the set of
    extrinsic languages?] \hfill
